Exchange Relations Examples

### 2021-03-29 rogers_exchange_relations_examples.tex
major overhaul in the sage folder

\section{Example 6: $S_3 * 1 \leftarrow 2 = P_3 + 1 \leftarrow 2 \rightarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,2,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,3,2,0) & \mu &= (3,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,22,34) \text{ and } \young(13,2).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & & \\
     & & & & 0 & 1 & & & \\
     & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & 0 & 1 & \\
     & & & & & & & s & c_3 \\
     & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are 2 restrictions coming from $X$ and 1 restriction from $X-s$. Indeed, we require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $\Sp\{e_1,e_4\} \subset \col X$. Furthermore, we require ${\color{red} a_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker(X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
    \item There are 2 restrictions from $X$. We need ${\color{red} b_4c_3 - sc_2 = b_2c_3 - sc_1 = 0}$ for $\ker X \subset \col X$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,a_3,b_1,b_3,b_2c_3,b_4c_3 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3 \rangle}$$
However, for the ideal $\langle c_3 \rangle$, we require $\dim \ker (X|_{s = 0}) = 3$ so we also need to include the equation ${\color{red} b_2c_2 - b_4c_1 = 0}$. Then the coordinate ring is really
$$\frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3,b_2c_2-b_4c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2,b_4 \rangle &\leadsto \young(1114,222,33) &\leadsto P_3 \\ 
    \langle c_3,b_2c_2-b_4c_1 \rangle &\leadsto \young(1113,222,34) &\leadsto 1 \leftarrow 2 \rightarrow 3
\end{array}
\]

@@

\section{Example 11: $1 \leftarrow 2 \rightarrow 3 * 1 \rightarrow 2 = 1 \leftarrow 2 \oplus P_1  + S_1 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,1,1,0) & \mu_1 &= (1,1,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,2,1,0) & \mu &= (2,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(13,2,4) \text{ and } \young(12,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
    0 & 1 & & & & & \\
     & s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & 0 & 1 & & & \\
     & & & s & b_3 & b_4 & c_2 \\
     & & & & 0 & 1 & \\
     & & & & & s & c_3 \\
     & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ but no restrictions from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_3 \in \ker X$.
    \item There are no restrictions from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_3 + sb_4 = 0}$ so that $e_5 + se_6 \in \ker (X-s)$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_1c_2-b_3c_1 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^3$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,b_3,c_3,b_1c_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2,b_4,c_1,c_2]}{\langle b_1 \rangle \cap \langle c_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_1 \rangle &\leadsto \young(1123,24,3) &\leadsto S_1 \oplus P_2 \\ 
    \langle c_2 \rangle &\leadsto \young(1123,23,4) &\leadsto 1 \leftarrow 2 \oplus P_1 
\end{array}
\]
\end{document}

>>>>

\section{Example 6: $S_3 * 1 \leftarrow 2 = P_3 + 1 \leftarrow 2 \rightarrow 3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,2,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,3,2,0) & \mu &= (3,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(11,22,34) \text{ and } \young(13,2).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & & \\
     & & & & 0 & 1 & & & \\
     & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & 0 & 1 & \\
     & & & & & & & s & c_3 \\
     & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 + s^2 e_3 \in \ker (X-s)$.
    \item There are 2 restrictions coming from $X$ and 1 restriction from $X-s$. Indeed, we require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $\Sp\{e_1,e_4\} \subset \col X$. Furthermore, we require ${\color{red} a_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker(X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
    \item There are 2 restrictions from $X$. We need ${\color{red} b_4c_3 - sc_2 = b_2c_3 - sc_1 = 0}$ for $\ker X \subset \col X$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,a_3,b_1,b_3,b_2c_3,b_4c_3 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3 \rangle}$$
However, for the ideal $\langle c_3 \rangle$, we require $\dim \ker (X|_{s = 0}) = 3$ so we also need to include the equation ${\color{red} b_2c_2 - b_4c_1 = 0}$ \rcom{this equation shows up in the script, so it's one of the minors}. Then the coordinate ring is really
$$\frac{\CC[b_2,b_4,c_1,c_2,c_3]}{\langle b_2,b_4 \rangle \cap \langle c_3,b_2c_2-b_4c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2,b_4 \rangle &\leadsto \young(1114,222,33) &\leadsto P_3 \\ 
    \langle c_3,b_2c_2-b_4c_1 \rangle &\leadsto \young(1113,222,34) &\leadsto 1 \leftarrow 2 \rightarrow 3
\end{array}
\]

@@

\section{Example 11: $1 \leftarrow 2 \rightarrow 3 * 1 \rightarrow 2 = 1 \leftarrow 2 \oplus P_1  + S_1 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,1,1,0) & \mu_1 &= (1,1,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (4,2,1,0) & \mu &= (2,2,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(13,2,4) \text{ and } \young(12,3).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cc;cc;cc;c}{cc;cc;cc;c}
    0 & 1 & & & & & \\
     & s & a_1 & a_2 & b_1 & b_2 & c_1 \\
     & & 0 & 1 & & & \\
     & & & s & b_3 & b_4 & c_2 \\
     & & & & 0 & 1 & \\
     & & & & & s & c_3 \\
     & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ but no restrictions from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_3 \in \ker X$.
    \item There are no restrictions from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_3 + sb_4 = 0}$ so that $e_5 + se_6 \in \ker (X-s)$.
    \item There are 2 restrictions from $X-s$. We need ${\color{red} c_3 = b_1c_2-b_3c_1 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,b_3,c_3,b_1c_2 \rangle} \cong \frac{\CC[a_2,b_1,b_2,b_4,c_1,c_2]}{\langle b_1 \rangle \cap \langle c_2 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_1 \rangle &\leadsto \young(1123,24,3) &\leadsto S_1 \oplus P_2 \\ 
    \langle c_2 \rangle &\leadsto \young(1123,23,4) &\leadsto 1 \leftarrow 2 \oplus P_1
\end{array}
\]

\section{Example 12: $1 \rightarrow 2 \leftarrow 3 * 1 \leftarrow 2 = 1 \rightarrow 2 \oplus P_3  + S_1 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,0,0) & \mu_2 &= (1,1,1,0) \\
    \lambda &= (5,3,1,0) & \mu &= (3,3,2,1)
\end{aligned}
\]
and the tableaux are
\[
\young(112,24,3) \text{ and } \young(13,2).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;c}{ccc;ccc;cc;c}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 \\
     & & & 0 & 1 & & & & \\
     & & & & 0 & 1 & & & \\
     & & & & & s & b_3 & b_4 & c_2 \\
     & & & & & & 0 & 1 & \\
     & & & & & & & s & c_3 \\
     & & & & & & & & 0
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker (X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
    \item There is 1 restriction from $X-s$. We need ${\color{red} b_4c_3 - sc_2 = 0}$ for $\ker (X-s) \subset \col (X-s)$.
\end{enumerate}
The minimal polynomial $X^3(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3]}{\langle a_1,a_2,b_1,b_3,b_4c_3 \rangle} \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3]}{\langle b_4 \rangle \cap \langle c_3 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_4 \rangle &\leadsto \young(11124,223,3) &\leadsto 1 \rightarrow 2 \oplus P_3 \\ 
    \langle c_3 \rangle &\leadsto \young(11123,224,3) &\leadsto S_1 \oplus P_2
\end{array}
\]

\section{Example 13: $1 \leftarrow 2 \rightarrow 3 * 2 \leftarrow 3 = 2 \rightarrow 3 \oplus P_3  + S_3 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (2,2,1,0) & \mu_1 &= (2,1,1,1) \\
    \lambda_2 &= (2,1,1,0) & \mu_2 &= (1,1,1,1) \\
    \lambda &= (4,3,2,0) & \mu &= (3,2,2,2)
\end{aligned}
\]
and the tableaux are
\[
\young(11,24,3) \text{ and } \young(13,2,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;cc;cc;cc}{ccc;cc;cc;cc}
    0 & 1 & & & & & & & \\
     & 0 & 1 & & & & & & \\
     & & s & a_1 & a_2 & b_1 & b_2 & c_1 & c_2 \\
     & & & 0 & 1 & & & & \\
     & & & & s & b_3 & b_4 & c_3 & c_4 \\
     & & & & & 0 & 1 & & \\
     & & & & & & s & c_5 & c_6 \\
     & & & & & & & 0 & 1 \\
     & & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 = 0}$ for $e_4 + se_5 \in \ker (X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_6 \in \ker X$.
    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$. We need ${\color{red} b_2c_5 - sc_1 = b_2c_6 - c_1 = 0}$ for $\ker X \subset \col X$. Furthermore, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^2(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5, c_1-b_2c_6,b_2c_3-b_4c_1 \rangle} \cong \frac{\CC[b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle b_2,c_1 \rangle \cap \langle c_1-b_2c_6, c_3-b_4c_6, b_2c_3-b_4c_1 \rangle}$$
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_2,c_1 \rangle &\leadsto \young(1114,223,34) &\leadsto 2 \rightarrow 3 \oplus P_3 \\ 
    \langle c_1-b_2c_6,c_3-b_4c_6,b_2c_3-b_4c_1 \rangle &\leadsto \young(1113,224,34) &\leadsto S_3 \oplus P_2
\end{array}
\]

\section{Example 14: $1 \rightarrow 2 \leftarrow 3 * 2 \rightarrow 3 = 2 \leftarrow 3 \oplus P_1  + S_3 \oplus P_2$}
Take 
\[\begin{aligned}
    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1) \\
    \lambda &= (5,4,2,0) & \mu &= (4,3,2,2)
\end{aligned}
\]
and the tableaux are
\[
\young(112,24,3) \text{ and } \young(11,23,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){cccc;ccc;cc;cc}{cccc;ccc;cc;cc}
    0 & 1 & & & & & & & & & \\
     & 0 & 1 & & & & & & & & \\
     & & 0 & 1 & & & & & & & \\
     & & -s^2 & 2s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 & c_2 \\
     & & & & 0 & 1 & & & & & \\
     & & & & & 0 & 1 & & & & \\
     & & & & & & s & b_3 & b_4 & c_3 & c_4 \\
     & & & & & & & 0 & 1 & & \\
     & & & & & & & & s & c_5 & c_6 \\
     & & & & & & & & & 0 & 1 \\
     & & & & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 + s^3e_4 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_5 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_5 + se_6 + s^2e_7 \in \ker (X-s)$.
    \item There are 2 restrictions from $X$ and 1 restriction from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_8 \in \ker X$. Furthermore, we need ${\color{red} a_2b_4 - s^2b_2 = a_3b_4 + sb_2 = 0}$ for $\Sp\{e_1 + se_2 +s^2e_3 + s^3e_4, e_5 + se_6 + s^2e_7\} \subset \col (X-s)$.
    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$. We need ${\color{red} b_4c_5 - sc_3 = 0}$ for $\ker X \subset \col X$. In addition, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^3(X-s)^2$ gives the additional equations ${\color{red} a_3c_3 = 0}$ and ${\color{red} c_1 + a_3c_4 + b_2c_6 = 0}$ so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5,a_3b_4,a_3c_3,b_2c_3-b_4c_1,c_1+a_3c_4+b_2c_6 \rangle}$$
$$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle a_3,b_2c_3-b_4c_1,c_1+b_2c_6 \rangle \cap \langle b_4,c_3,c_1+a_3c_4+b_2c_6 \rangle}$$
\rcom{The script also has the equations $b_4c_6 + c_3$ and $b_2c_3c_6 + c_1c_3$ in the ideal. With this, the decomposition is the same except the first ideal also has $b_4c_6 + c_3$. The tableaux we get remain the same.}
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle a_3,b_2c_3-b_4c_1,c_1+b_2c_6 \rangle &\leadsto \young(11113,2224,34) &\leadsto S_3 \oplus P_2 \\ 
    \langle b_4,c_3,c_1+a_3c_4+b_2c_6 \rangle &\leadsto \young(11112,2234,34) &\leadsto 2 \leftarrow 3 \oplus P_1
\end{array}
\]

\section{Example 15: $1 \rightarrow 2 \leftarrow 3 * 1 \leftarrow 2 \rightarrow 3 = S_1 \oplus S_3 \oplus P_2 + P_1 \oplus P_3$}
Take 
\[\begin{aligned}
    \lambda_1 &= (3,2,1,0) & \mu_1 &= (2,2,1,1) \\
    \lambda_2 &= (2,1,1,0) & \mu_2 &= (1,1,1,1) \\
    \lambda &= (5,3,2,0) & \mu &= (3,3,2,2)
\end{aligned}
\]
and the tableaux are
\[
\young(112,24,3) \text{ and } \young(13,2,4).
\]
The matrix in consideration is:
\[
X = \left[\begin{BMAT}(e){ccc;ccc;cc;cc}{ccc;ccc;cc;cc}
    0 & 1 & & & & & & & & \\
     & 0 & 1 & & & & & & & \\
     & & s & a_1 & a_2 & a_3 & b_1 & b_2 & c_1 & c_2 \\
     & & & 0 & 1 & & & & & \\
     & & & & 0 & 1 & & & & \\
     & & & & & s & b_3 & b_4 & c_3 & c_4 \\
     & & & & & & 0 & 1 & & \\
     & & & & & & & s & c_5 & c_6 \\
     & & & & & & & & 0 & 1 \\
     & & & & & & & & & s
\end{BMAT}
\right]
\]
\begin{enumerate}[label=\boxed{\arabic*}:]
    \item There are no restrictions here, but we have $e_1 \in \ker X$ and $e_1 + se_2 +s^2e_3 \in \ker (X-s)$.
    \item There is 1 restriction coming from $X$ and 1 restriction from $X-s$. We require ${\color{red} a_1 = 0}$ for $e_4 \in \ker X$ and ${\color{red} a_2 + sa_3 = 0}$ for $e_4 + se_5 + s^2e_6 \in \ker (X-s)$.
    \item There are 2 restrictions from $X$ but no restrictions from $X-s$. We need ${\color{red} b_1 = b_3 = 0}$ so that $e_7 \in \ker X$.
    \item There is 1 restriction from $X$ and 2 restrictions from $X-s$. We need ${\color{red} b_4c_5 - sc_3 = 0}$ for $\ker X \subset \col X$. In addition, we need ${\color{red} c_5 + sc_6 = 0}$ and ${\color{red} b_2c_3 - b_4c_1 + s(b_2c_4 - b_4c_2) = 0}$ so that $\dim \ker (X-s) = 3$.
\end{enumerate}
The minimal polynomial $X^3(X-s)^2$ does not give any new equations so our coordinate ring after taking $s \rightarrow 0$ is
$$\frac{\CC[a_1,a_2,a_3,b_1,b_2,b_3,b_4,c_1,c_2,c_3,c_4,c_5,c_6]}{\langle a_1,a_2,b_1,b_3,c_5,c_3+b_4c_6,b_2c_3-b_4c_1 \rangle}$$
$$ \cong \frac{\CC[a_3,b_2,b_4,c_1,c_2,c_3,c_4,c_6]}{\langle b_4,c_3 \rangle \cap \langle b_2c_6-c_1,c_3+b_4c_6 \rangle}$$
\rcom{The script also has the equation $b_2c_3c_6 + c_1c_3$ in the ideal. In the decomposition, the second ideal also has $b_2c_3 - c_1b_4$. The corresponding tableaux are unchanged.}
The corresponding tableau for each ideal is:
\[\begin{array}{ccc}\vspace{1mm}
    \langle b_4,c_3 \rangle &\leadsto \young(11124,223,34) &\leadsto P_1 \oplus P_3 \\
    \langle b_2c_6-c_1,c_3+b_4c_6 \rangle &\leadsto \young(11123,224,34) &\leadsto S_1 \oplus S_3 \oplus P_2
\end{array}
\]
\end{document}
